Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
zlog intro
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

>>>>

We evaluate the mapping of ZLog onto Malacology by examining the costs of
utilizing the metadata service as a sequencer, and propogating interface
changes throughout the cluster using the monitoring service. We have omitted
evaluation of the overhead costs of adding object interfaces themselves due to
lack of space, and the fact that they are heavily tested and used already in
production with acceptable performance, introducing a small constant overhead
per operation but otherwise does not affect scalability.
